\documentclass{article}
\usepackage{fontspec}
\defaultfontfeatures{Mapping=tex-text, Scale=MatchLowercase}
\setmainfont{Minion Pro}
\setmonofont{Consolas}
\usepackage[letterpaper, textwidth=5.5in, textheight=9in]{geometry}
\usepackage{hyperref}
\usepackage{sectsty}
\sectionfont{\mdseries\large}
\usepackage{enumitem}
% Lists with hanging indents
\newlist{hdesc}{description}{1}
\setlist[hdesc]{format=\small\mdseries\scshape, align=right,
  labelindent=-4.45em, itemindent=0pt, labelwidth=4em, leftmargin=!,
  itemsep=0pt}
\newlist{henum}{enumerate}{1}
\setlist[henum]{label=\arabic*., labelwidth=4em, labelindent=-4.45em,
  itemindent=0pt, leftmargin=!, itemsep=0pt}

\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}
{\LARGE Abhishek Sarkar\vspace{1em}}\\
Cummings Life Science Center 412\\
920 E. 58th St.\\
Chicago, IL 60615\vspace{1em}

\begin{hdesc}
\item[email] \url{aksarkar@alum.mit.edu}
\item[url] \url{https://aksarkar.github.io}
\end{hdesc}

\section*{Research interests}
Machine learning, Bayesian inference, regulatory genomics, epigenomics, complex traits

\section*{Education}
\begin{hdesc}
\item[2017] Ph.D.\ Computer Science, Massachusetts Institute of Technology
\item[2013] M.S.\ Computer Science, Massachusetts Institute of Technology
\item[2011] B.S.\ Computer Science with Highest Honors, University of North
  Carolina at Chapel Hill
\end{hdesc}

\section*{Research experience}
\begin{hdesc}[itemsep=1em]
\item[2017--] \textbf{University of Chicago}\\
Postdoctoral Scholar\\
Matthew Stephens (PI)\\
Human Genetics Department
\end{hdesc}
\begin{hdesc}[itemsep=1em]
\item[2011--2017] \textbf{Massachusetts Institute of Technology}\\
Research Assistant\\
Computational Biology Group, Manolis Kellis (PI)\\
Computer Science and Artificial Intelligence Lab
\end{hdesc}

\section*{Teaching experience}
\begin{hdesc}[itemsep=1em]
\item[2014] Teaching assistant, ``Computational Biology: Genomes, Networks, Evolution'' (fall)
\end{hdesc}

\section*{Pre-prints}
\begin{henum}
\item Yongjin Park$^*$, \textbf{Abhishek Sarkar$^*$}, et al. ``A Bayesian
  approach to mediation analysis predicts 206 causal target genes in
  Alzheimer's disease.'' \emph{BioRxiv} (2017) \emph{*Equal
  contribution}
\item Yongjin Park$^*$, \textbf{Abhishek K. Sarkar}$^*$, et al. ``Multi-tissue
  polygenic models for transcriptome-wide association studies.''
  \emph{BioRxiv}. (2017) \emph{*Equal contribution}
\end{henum}

\section*{Peer-reviewed publications}
\begin{henum}
\item Yaping Liu, \textbf{Abhishek Sarkar}, Pouya Kheradpour, Jason Ernst, and
  Manolis Kellis. ``Evidence of reduced recombination rate in human regulatory
  domains.'' \emph{Genome Biology}. (2017)
\item Felix Day, \ldots, \textbf{Abhishek K.\ Sarkar}, et al. ``Genomic
  analyses for age at menarche identify 389 independent signals and indicate
  BMI-independent effects of puberty timing on cancer susceptibility.''
  \emph{Nat Genet}. (2017) \emph{Author 9/215}
\item Roadmap Epigenomics Consortium et al. ``Integrative analysis of 111
  reference human epigenomes.'' \emph{Nature}, 518(7539), 317–330 (2015).
  \emph{Integrative analysis lead (equal contributor)}.
\end{henum}

\section*{Presentations}
\begin{henum}
\item Yongjin Park$^*$, \textbf{Abhishek Sarkar$^*$}, Liang He$^*$ and Manolis
  Kellis. "Variational Bayes inference algorithm for causal multivariate
  mediation with linkage disequilibrium." Workshop on Machine Learning in
  Computational Biology, Thirty-first Annual Conference on Neural Information
  Processing Systems, Los Angeles, California, USA. 2017. \emph{$^*$Equal contribution}
\item Yongjin Park$^*$, \textbf{Abhishek Sarkar$^*$}, Liang He$^*$ and Manolis
  Kellis. ``Identification transcriptomic and epigenetic mediators in
  Alzheimer's disease: Bayesian inference and causal mediation analysis of
  regulatory programs in GWAS statistics.'' 69\textsuperscript{th} meeting of
  the American Society of Human Genetics, Orlando, Florida, USA. 2017 \emph{$^*$Equal contribution}
\item Yongjin Park$^*$, \textbf{Abhishek Sarkar$^*$}</strong>, Kunal Bhutani,
  Manolis Kellis. "Multi-tissue polygenic models for transcriptome-wide
  association studies" (talk). Biology of Genomes, Cold Spring Harbor
  Laboratory, Cold Spring Harbor, NY, 2017. \emph{$^*$Equal contribution}
\item \textbf{Abhishek Sarkar}, Yongjin Park, Manolis Kellis. ``Dissecting the
  non-infinitesimal architecture of complex traits using group spike-and-slab
  priors'' (contributed talk). Workshop on Machine Learning in Computational
  Biology, Thirtieth Annual Conference on Neural Information Processing
  Systems, Barcelona, Spain. 2016.
\item \textbf{Abhishek Sarkar}, Yongjin Park, Manolis Kellis. ``Dissecting the
  non-infinitesimal architecture of complex traits'' (poster).
  68\textsuperscript{th} meeting of the American Society of Human Genetics,
  Vancouver, Canada. 2016.
\item \textbf{Abhishek Sarkar}, Luke Ward, Manolis Kellis. ``Functional
  enrichments of disease variants across thousands of independent loci in eight
  diseases.'' (talk). Leena Peltonen School of Human Genomics, Wellcome Trust
  Sanger Institute, Hinxton, Cambridge, UK. 2016.
\item Yongjin Park, \textbf{Abhishek Sarkar}, Nick Mancuso, Alexander Gusev,
  Bogdan Pasaniuc, Manolis Kellis. ``Computational discovery of epigenetic
  mediators in Alzheimer’s disease from imputed methyome-wide association
  statistics'' (poster). The Biology of Genomes, Cold Spring Harbor, NY, USA.
  2016.
\item Kunal Bhutani$^*$, \textbf{Abhishek Sarkar}$^*$, Yongjin Park, Manolis
  Kellis, Nicholas Schork. ``Propagating uncertainty of predicted expression in
  transcriptome-wide association studies'' (poster). The Biology of Genomes,
  Cold Spring Harbor, NY, USA. 2016. \emph{$^*$Equal contribution}
\item \textbf{Abhishek Sarkar}, Lucas D.\ Ward, Manolis Kellis.
  ``Regulatory annotations implicate thousands of independent loci'' (poster).
  67\textsuperscript{th} meeting of the American Society of Human Genetics,
  Baltimore, MD, USA. 2015.
\item \textbf{Abhishek K.\ Sarkar}, Lucas D.\ Ward, Manolis
  Kellis. ``Genome-wide enrichments for regulatory regions across thousands of
  unlinked disease-associated variants'' (poster). 65\textsuperscript{th}
  meeting of the American Society of Human Genetics, Boston, MA, USA. 2013.
\item Vineeta Agarwala, \textbf{Abhishek Sarkar}, Kyle Gaulton. ``Using the
  Epigenome Roadmap data to analyze genetic studies of Type 2 Diabetes''
  (workshop talk). 65\textsuperscript{th} meeting of the American Society of
  Human Genetics, Boston, MA, USA. 2013.
\item \textbf{Abhishek K.\ Sarkar}, Lucas D.\ Ward, Manolis
  Kellis. ``Systematically interpreting GWAS using regions from Roadmap''
  (poster). Epigenomics: A Roadmap to the Living Genome, Boston, MA, USA. 2013.
\item Lucas Ward, \textbf{Abhishek Sarkar}, Manolis Kellis. ``Global
  contributions of regulatory elements to disease risk and evolutionary fitness
  in the human population'' (poster). 5\textsuperscript{th} annual RECOMB
  Conference on Regulatory and Systems Genomics, San Francisco, CA, USA. 2012.
\item \textbf{Abhishek Sarkar}. ``Functional GWAS enrichments across tens of
  thousands of enhancer elements'' (talk). Epigenomics Seminar Series, Broad
  Institute, Cambridge, MA, USA. 2011.
\end{henum}

\section*{Technical reports}
\begin{henum}
\item Kunal Bhutani, \textbf{Abhishek Sarkar}, et al. ``Modeling prediction
  error improves power of transcriptome-wide association studies.''
  \emph{BioRxiv}. (2017) \emph{*Equal contribution}
\item \textbf{Abhishek K.\ Sarkar}, Lucas D.\ Ward, Manolis Kellis.
  ``Functional enrichments of disease variants across thousands of independent
  loci in eight diseases.'' \emph{BioRxiv}. (2016)
\end{henum}

\section*{Honors}
\begin{hdesc}
\item[2016] Accepted to Leena Peltonen School of Human Genomics
\item[2011] Awarded NSF Graduate Research Fellowship
\item[2011] Inducted into Phi Beta Kappa honors fraternity
\end{hdesc}

\end{document}
